---
title: "Data processing"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries and helpers, include=FALSE}

library(dplyr)
library(googlesheets4)
library(ggplot2)
library(tidyr)
library(dm)
library(lubridate)
source("helper/data_clean.R")
source("helper/unpreditability_future_scale_processing.R")
source("helper/career_indecision_scale_processing.R")

```

# 0. Loading raw data

Raw data is loaded from googlesheets. The console will require you to authenticate. After loading we change column names to facilitate data wrangling using 

```{r}

raw_data <- read_sheet("https://docs.google.com/spreadsheets/d/1CWdU5igjqq7nusOeyu75MnjIjGMejDUz3bwWHB-wRJM/edit?gid=1573672169#gid=1573672169") 

raw_data <- clean_colnames(raw_data)%>% 
  select(-`N° de participante`)

```

# 1. Split raw data into related dataframes

We want this to have a relational database schema to facilitate future access

# 1.1. Subject info

```{r}


subject_info_raw <- raw_data %>% 
  select(ID, gender, birth_date) %>% 
  mutate(birth_date = lubridate::ymd(as.Date(birth_date))) %>% 
  mutate(age_months = interval(birth_date, today()) %/% months(1))%>% 
  mutate(age_years = time_length(interval(birth_date, today()), "years"))


```

## 1.2. home environment

```{r}

home_environment_raw <- raw_data %>% 
  select(ID, max_educ_level_mother, max_educ_level_father) %>% 
  mutate(max_educ_level_mother_num = case_when(
    max_educ_level_mother == "Primario incompleto" ~ 1,
        max_educ_level_mother == "Primario completo" ~ 2,
        max_educ_level_mother == "Secundario incompleto" ~ 3,
        max_educ_level_mother == "Secundario completo" ~ 4,
        max_educ_level_mother == "Terciario incompleto" ~ 5,
        max_educ_level_mother == "Terciario completo" ~ 6,
        max_educ_level_mother == "Terciario en curso" ~ 7,
        max_educ_level_mother == "Universitario incompleto" ~ 8,
        max_educ_level_mother == "Universitario completo" ~ 9,
        max_educ_level_mother == "Posgrado incompleto" ~ 10,
        max_educ_level_mother == "Posgrado completo" ~ 11,
  ))%>% 
  mutate(max_educ_level_father_num = case_when(
    max_educ_level_father == "Primario incompleto" ~ 1,
        max_educ_level_father == "Primario completo" ~ 2,
        max_educ_level_father == "Secundario incompleto" ~ 3,
        max_educ_level_father == "Secundario completo" ~ 4,
        max_educ_level_father == "Terciario incompleto" ~ 5,
        max_educ_level_father == "Terciario completo" ~ 6,
        max_educ_level_father == "Terciario en curso" ~ 7,
        max_educ_level_father == "Universitario incompleto" ~ 8,
        max_educ_level_father == "Universitario completo" ~ 9,
        max_educ_level_father == "Posgrado incompleto" ~ 10,
        max_educ_level_father == "Posgrado completo" ~ 11,
  ))

```

## 1.3. MacArthur Scale

```{r}

mac_arthur_scale_raw <- raw_data %>% 
  select(ID, society_ladder)


```

## 1.4. Unpredictability

```{r}

future_unpredictability_raw <- unpredictability_future_processing(raw_data) %>% 
  select(-item_text)

future_unpredictability_items <- unpreditability_future_items(raw_data)

```


## 1.5. Career indecision

```{r}

career_indecision_raw <- raw_data %>% 
  select(ID, contains("CIP_")) %>% 
  career_indecision_processing() 

career_indecision_items <- career_indecision_items()

```


# Plot relational schema

```{r}

current_dm <- dm(subject_info_raw,
                 home_environment_raw, 
                 mac_arthur_scale_raw,
                 future_unpredictability_raw, future_unpredictability_items,
                 career_indecision_raw, career_indecision_items) %>%
  # dm_enum_pk_candidates(career_indecision_items)
  dm_add_pk(subject_info_raw, ID) %>%              
  dm_add_pk(future_unpredictability_raw, item_name) %>% 
  dm_add_pk(career_indecision_raw, item_name) %>% 
  dm_add_fk(home_environment_raw, ID, subject_info_raw) %>%  
  dm_add_fk(mac_arthur_scale_raw, ID, subject_info_raw)   %>% 
  dm_add_fk(future_unpredictability_raw, ID, subject_info_raw) %>%
  dm_add_fk(future_unpredictability_items, item_name, future_unpredictability_raw)%>%
  dm_add_fk(career_indecision_raw, ID, subject_info_raw) %>% 
  dm_add_fk(career_indecision_items, item_name, career_indecision_raw)


my_dm_draw <- function(dm, rankdir = "RL", view_type = "all") {
  data_model <- dm:::dm_get_data_model(dm, FALSE)
  graph <- dm:::bdm_create_graph(
    data_model,
    rankdir      = rankdir,
    view_type    = view_type,
    columnArrows = TRUE,
    graph_attrs  = "",
    node_attrs   = "",
    edge_attrs   = "",
    graph_name   = "Data Model",
    font_size    = list()
  )
  
  # Inject layout options into the DOT string
  dot <- graph$dot_code
  dot <- gsub(
    "graph \\[",
    "graph [splines=polyline nodesep=1 ranksep=1.5 ",
    dot
  )
  
  DiagrammeR::grViz(dot)
}

(relational_database_plot <- my_dm_draw(current_dm))

library(DiagrammeRsvg)
library(rsvg)


relational_database_plot%>%
  export_svg() %>%
  charToRaw() %>%
  rsvg_png("relational_database_plot.png")


```


# Save data into csv's

```{r}

write.csv(subject_info_raw, "data/data_raw/subject_info_raw.csv", row.names = F)

write.csv(home_environment_raw, "data/data_raw/home_environment_raw.csv", row.names = F)

write.csv(mac_arthur_scale_raw, "data/data_raw/mac_arthur_scale_raw.csv", row.names = F)

write.csv(future_unpredictability_raw, "data/data_raw/future_unpredictability_raw.csv", row.names = F)

write.csv(future_unpredictability_items, "data/data_raw/future_unpredictability_items.csv", row.names = F)

write.csv(career_indecision_raw, "data/data_raw/career_indecision_raw.csv", row.names = F)

write.csv(career_indecision_items, "data/data_raw/career_indecision_items.csv", row.names = F)

```














